An Open Platform for Managing Short Programming Exercises

### 2013-06-20 paper/paper.tex
edited the abstract

We have built CloudCoder, an open platform for creating, assigning, and sharing
short programming exercises for a variety of languages (we currently
support C/C++, Java, Python and Ruby, and can add others).  Like other
systems, CloudCoder is a web service that lets
students write code directly in their web browser, click the
``submit'' button, and receive immediate feedback.  Unlike other
systems, which tend to be closed, or commercial, or both, CloudCoder
is a completely open platform.  The code for the system is
open-source, and exercises written for CloudCoder are shared to a
central repository under a permissive Creative Commons license
(BY-SA).  Finally, CloudCoder collects detailed data that faculty can use for
educational research.

In this work, we report on successful pilot studies of CloudCoder at several
institutions.  We also describe on-going work to create a ``hint'' system
for CloudCoder, similar to what one would expect from an Intelligent
Tutoring System (ITS).

@@

\section{Discussion Questions}

>>>>

We have built CloudCoder, an open platform for creating, assigning, and sharing
short programming exercises for a variety of languages (currently C/C++, Java,
Python and Ruby).  Like other similar systems, CloudCoder is web-based,
letting students write code directly in a web browser, click the
``submit'' button, and receive immediate feedback.  Unlike other
systems, which tend to be closed, or commercial, or both, CloudCoder
is a completely open platform.  The code for the system is
open-source, and exercises written for CloudCoder are shared to a
central repository under a permissive Creative Commons license
(BY-SA).  Finally, CloudCoder collects detailed data that faculty can use for
educational research.

In this paper, we report on successful pilot studies of CloudCoder at several
institutions.
% We also describe on-going work to create a ``hint'' system
%for CloudCoder, similar to what one would expect from an Intelligent
%Tutoring System (ITS).
We also outline some research questions we hope to address in future work.

@@

\section{Questions}
